### 2014-11-12 paper_dec/paper_dec.tex
Eerste beetje HBase

\begin{document}
\section{Cassandra}

@@

%afronden

>>>>

\begin{document}
\section{Columnar stores}
\subsection{Cassandra}

@@

\subsection{HBase}

Apache HBase is an open source datastore using Google BigTable's datamodel, but running on top of the Hadoop Distributed File System (HDFS) instead of the Google File System (GFS).
\\Since its launch, HBase has adopted several secondary indexing mechanisms. HBase doesn't offer an SQL-like advanced querying language, but because of its HDFS underpinnings it can function as both input and output for Map/Reduce jobs.
\\The strong points of HBase are its strong consistency, which is rare among NoSQL-stores, and its concurrency model: ACID-compliant single row transactions and optimistic concurrency control using multiversioning for wider scope transactions\cite{hbase_acid}\cite{grolinger2013data}\cite{borthakur2011apache}.
